### 2019-05-10 2-Chapters/4-Chapter/IEEE_WCNC_2019__DemoICT.git/main.tex
Added two references, as suggested by Christophe.

\paragraph{Related works.}
% FIXME?
% \TODOL{Est-ce que je fais ça ici ou à la fin du chapitre 5 ? Ou peut-être en chapitre 1, ça ferait du contenu au chapitre 1...}
%
We evoke quickly here some previous works that similarly implemented proof-of-concepts to show that reinforcement learning algorithms can be used within real-world wireless communications.
In $2015$ and $2016$, a PhD student (Navikkumar Modi) and post-doc (Sumit J. Darak) in our team SCEE worked with Christophe Moy and others for the following publications,
\cite{darak2016bayesian,Darak16,modiDemo2016,kumar2016two}.
Since $2017$, Sumit J. Darak and his team at IIIT Delhi have been very active in the research on cognitive radio using multi-armed bandits, and some of their recent works are illustrated with real-world demo using USRP and the MATLAB/Simulink system
\cite{KumarYadav2018,SawantKumar2018,JoshiKumar2018}.

>>>>

\paragraph{Related works.}
% FIXME?
% \TODOL{Est-ce que je fais ça ici ou à la fin du chapitre 5 ? Ou peut-être en chapitre 1, ça ferait du contenu au chapitre 1...}
%
We evoke quickly here some previous works that similarly implemented proof-of-concepts to show that reinforcement learning algorithms can be used within real-world wireless communications.
Starting from $2010$, the works of Wassim Jouini \cite{Jouini09,Jouini10,Jouini12} were the first ones to propose to use Reinforcement Learning for Cognitive Radio, especially MAB and the \UCB{} algorithm, and from $2014$, proof-of-concepts were developed by Christophe Moy and his student Clément Robert \cite{RobertSDR2014,MoyWSR2014}.
In $2015$ and $2016$, Christophe Moy continued to work on this direction, with a PhD student (Navikkumar Modi) and post-doc (Sumit J. Darak) in our team SCEE, for the following publications
\cite{darak2016bayesian,Darak16,modiDemo2016,kumar2016two}.
Since $2017$, Sumit J. Darak and his team at IIIT Delhi have been very active in the research on cognitive radio using multi-armed bandits, and some of their recent works are illustrated with real-world demo using USRP and the MATLAB/Simulink system
\cite{KumarYadav2018,SawantKumar2018,JoshiKumar2018}.

### 2019-05-10 2-Chapters/5-Chapter/chapter5.tex
Added two references, as suggested by Christophe.

% FIXME much more details?
Other works in the same line of research included \cite{modiDemo2016} implemented using the same USRP testbed as for our demonstration in Chapter~\ref{chapter:4} (Section~\ref{sec:4:gnuradio}),
and the first work of a research team based in IIT Dehli, \cite{kumar2016two}.
%
More recent works by the same team, \cite{KumarYadav2018,SawantKumar2018,JoshiKumar2018}, all follow the same approach and include an experimental section that shows the results of an implementation of the proposed algorithms on USRP boards.
% \TODOL{I should explain more, no? Who does what and why? So long...}

>>>>

% % FIXME much more details?
% Other works in the same line of research included \cite{modiDemo2016} implemented using the same USRP testbed as for our demonstration in Chapter~\ref{chapter:4} (Section~\ref{sec:4:gnuradio}),
% and the first work of a research team based in IIT Dehli, \cite{kumar2016two}.
% %
% More recent works by the same team, \cite{KumarYadav2018,SawantKumar2018,JoshiKumar2018}, all follow the same approach and include an experimental section that shows the results of an implementation of the proposed algorithms on USRP boards.
% % \TODOL{I should explain more, no? Who does what and why? So long...}
